Stateless Model Checking with Data-Race Preemption Points

### 2015-10-02 pldi-16/evaluation.tex
make structure for evaluation

@@

% TODO: Don't forget to add to quicksand

Evaluation questions:
\begin{enumerate}
	\item Easy question: Is it good to incorporate DR analysis for new PPs? (Do we find DR-PP-only bugs?)
	\item How does this compare to static DR detection (how many DRs does ID verify as benign?)
	\item DRs aside, is ID more effective than the maximal state space? (Do we find bugs in subset spaces, when the max state space would time out?)
		% Make sure to argue how this shows ID is applicable to e.g. message-passing SMC tools. "Even when DR PPs aren't on the table, you should do our thing."
	\item Is ID useful for managing new DR PPs? (Are there some DRs where the PP alone finds the bug, and others where the old PP plus the new DR PP is needed?)
		% How many DR bugs were found from DR-alone state space, and how many from sema_foo + DR state space? What we want is a *variety*, which proves that iterative deepening is better than either individual strategy.
	\item How effective is the free-re-malloc technique at eliminating false positives? (Just turn the optimization off, and measure how many more SSes are generated.)

% Figure out concretely what the data race tricks are that we do, so we can claim them as contributions in the paper. Then ACTUALLY EVALUATE THEM.
%         - Speculative DR PPs.
%                 Not a heuristic, rather how to make it work at all to begin with.
%                 (Cite MS thesis, claim on backwards explorating finding bugs faster)
%         - Free/re-malloc to eliminate some false positives. See #193.
%                 Measure how many false positives are eliminated.
%                 Check, ofc, to make ABSOLUTE SURE, that no bugs missed w/ this trick.
%                         If there are, it could be because of the implementation
%                         bug described in #193.
%         - Using tid/last_call filtering because whole stack traces are too expensive.
%                 Turn on/off and measure how resulting DR bug #s change.
%         - Optional: Reprioritizing DRs based on "confirmed" / "suspected"
%                 Shouldn't be hard just make ID wrapper print "s" or "c"!
%                 Is it helpful for ID to put priorities on DR PPs?
%                         Test by inverting the priority and see if fewer buges are found.
%         // Super optional to talk about. Probably not worth the time.
%         // - "Too suspicious" (during init/destroy)
%         //      (Cite eraser, section 2.2)

%% Notes from jiri meeting. Some overlap with stuff above.
% Evaluation in 2 major questions
%         Data races (Sequence this first) vs no-DR-systesting
%                 Sub questions: Compare to single-pass DRs
%                         What false positive rate are we avoiding by comparison?
%                         How often would the DR not even be caught on the 1st execution, requiring backtracks to expose?
%                                 (don't forget set EXPLORE_BACKWARDS=0 here)
%         "Control experiment vs ID" (PLDI cares less asbout "finding bugs faster")

\end{enumerate}

>>>>

% TODO: Abbreviate SMC, and fixed-PP approach.

@@

% TODO: Don't forget to add to quicksand a feature to print time-when-job-started (ie, tell total time from test start to bug found in a DR state space == job-start time + job-elapsed time)
% TODO ******BEFORE****** you begin running experimence en masse!

Although \quicksand~presents Iterative Deepening and data-race PPs as interconnected techniques, they each could theoretically be employed alone in other model checkers.
For example, a single-state-space tool could use data-race candidates during immediately subsequent interleavings, essentially changing the state space on the fly.
Likewise, a message-passing-only tool could employ Iterative Deepening despite data races being absent from its concurrency model.
Hence, though many of our experiments compare \quicksand~to the state-of-the-art as a whole,
we also sought to evaluate each technique individually.
Our evaluation answers the following questions:
\begin{enumerate}
	\item Is combining data-race analysis with stateless model checking productive?
		\begin{enumerate}
			\item Do data-race PPs expose new bugs that couldn't be found with single-state-space model checking?
				% Elaborate later:
				% Among those, how many were missed in a {\em completed} execution of the otherwise ``maximal'' state space?
			\item Do we avoid false positives compared to single-pass?
				% Explain later as:
				% How many data-race candidates were verified as benign
				% Also Include:
				% How many false positives does the free-re-malloc technique suppress?
			% TODO: This one's optional. You can give up on it.
			\item Do we avoid false negatives compared to single-pass?
				% Explain later as: How many data-race bugs required backtracking to be identified as candidates in the first place
				%(don't forget set EXPLORE_BACKWARDS=0 here)
		\end{enumerate}
	\item Is Iterative Deepening better than the single-state-space model?
		\begin{enumerate}
			\item Does Iterative Deepening find bugs
				% in subset state spaces
				faster than the single-state-space approach, even without data races?
			\item Does Iterative Deepening help test data-race PPs?
				% Are there some DRs where the PP alone finds the bug, while the superset SS cannot, and some vice versa?
				% What we want is a *variety*, which proves that iterative deepening is better than either individual strategy.
		\end{enumerate}
\end{enumerate}

\subsection{Evaluating Data-Race PPs}

\subsection{Evaluating Iterative Deepening}

% Figure out concretely what the data race tricks are that we do, so we can claim them as contributions in the paper. Then ACTUALLY EVALUATE THEM.
%         - Speculative DR PPs.
%                 Not a heuristic, rather how to make it work at all to begin with.
%                 (Cite MS thesis, claim on backwards explorating finding bugs faster)
%         - Free/re-malloc to eliminate some false positives. See #193.
%                 Measure how many false positives are eliminated.
%                 Check, ofc, to make ABSOLUTE SURE, that no bugs missed w/ this trick.
%                         If there are, it could be because of the implementation
%                         bug described in #193.
%         - Using tid/last_call filtering because whole stack traces are too expensive.
%                 Moderately optional, 1st priority since theoretically interesting:
%                 Turn on/off and measure how resulting DR bug #s change.
%         - Optional: Reprioritizing DRs based on "confirmed" / "suspected"
%                 Shouldn't be hard just make ID wrapper print "s" or "c"!
%                 Is it helpful for ID to put priorities on DR PPs?
%                         Test by inverting the priority and see if fewer buges are found.
%         // Super optional to talk about. Probably not worth the time.
%         // - "Too suspicious" (during init/destroy)
%         //      (Cite eraser, section 2.2)
